Data_extractions

### 2019-02-07 R/Data_extractions.Rmd
updated file sub-directories and bold/italic formatting

Let's try to extract data from:   
 1. Figure 2a in the paper by Weil et al. 2006: Immune challenge retards seasonal reproductive regression in rodents: evidence for terminal investment (**Weil2006.pdf**)   
 2. Figure 2a in the paper by Sadd et al. 2006: Modulation of sexual signalling by immune challenged male mealworm beetles (*Tenebrio molitor*, L.): evidence for terminal investment and dishonesty (**Sadd2006.pdf**)

@@

```{r save metadigitise, eval=FALSE, message = FALSE}
write.csv(data, file = "filename.csv")
```

@@

With these two papers we just extracted, we had a relatively easy job. There were descriptive statistics values reported in the plots. If we cannot get means and standard errors (or SD) from the text, tables and figures (or already-calculated effect sizes, which is still rare), we can look for test (inferential) statistics. Test statistics that are usable include t-values form t-tests, F-values, Chi-square values, and p-values. These values from simple statistical tests (like independent or paired t-tests) are easily convertible into SMD (d, g) or r (correlation coefficient). These conversions and some others can be calculated in R if you know the formulas (including conversion from SMD to correlation coefficient), but for the exercise purpose we will use this web-based Practical Meta-Analysis Effect Size Calculator:   
https://www.campbellcollaboration.org/research-resources/research-for-resources/effect-size-calculator.html

```{r webEScalcualtor, echo=FALSE, fig.cap=" ", out.width='100%'}
knitr::include_graphics("./images/webEScalcualtor.png")
```

@@

**TASK 5**:   
Using the web-based effect size calculator, estimate a few other effect sizes using test (inferential) statistics reported in Sadd2006.

@@

The *compute.es* function inputs and names are as follows:   
 * ANCOVA F-test: "a.fes()""   
 * ANCOVA means: "a.mes()"   
 * ANCOVA means (pooled sd): "a.mes2()"   
 * ANCOVA p-value: "a.pes()"    
 * ANCOVA t-test: "a.tes()"   
 * Chi-squared (1 df): "chies()"   
 * Correlation: "res()"    
 * d-statistic: "des()"    
 * Failure group (binary): "failes()"    
 * F-test: "fes()"   
 * Log odds ratio: "lores()"    
 * Means: "mes()"    
 * Means (pooled sd): "mes2()"   
 * Proportions (binary): "propes()"    
 * p-value: "pes()""    
 * t-test: "tes()""    
To learn more see the package vignette or https://www.rdocumentation.org/packages/compute.es/versions/0.2-4/topics/compute.es-package

>>>>

Let's try to extract data from (all pdf files are located in the "pdf" sub-folder):   
 1. Figure 2a in the paper by Weil et al. 2006: Immune challenge retards seasonal reproductive regression in rodents: evidence for terminal investment (**Weil2006.pdf**)   
 2. Figure 2a in the paper by Sadd et al. 2006: Modulation of sexual signalling by immune challenged male mealworm beetles (*Tenebrio molitor*, L.): evidence for terminal investment and dishonesty (**Sadd2006.pdf**)

@@

```{r save metadigitise, eval=FALSE, message = FALSE}
write.csv(data, file = "filename.csv") #adjust the file name and path as needed
```

@@

With these two papers we just extracted, we had a relatively easy job. There were descriptive statistics values reported in the plots. If we cannot get means and standard errors (or SD) from the text, tables and figures (or already-calculated effect sizes, which is still rare), we can look for test (inferential) statistics. Test statistics that are usable include t-values form t-tests, F-values, Chi-square values, and p-values. These values from simple statistical tests (like independent or paired t-tests) are easily convertible into SMD (*d*, *g*) or r (correlation coefficient). These conversions and some others can be calculated in R if you know the formulas (including conversion from SMD to correlation coefficient), but for the exercise purpose we will use this web-based Practical Meta-Analysis Effect Size Calculator:   
https://www.campbellcollaboration.org/research-resources/research-for-resources/effect-size-calculator.html

```{r webEScalcualtor, echo=FALSE, fig.cap=" ", out.width='100%'}
knitr::include_graphics("../images/webEScalcualtor.png")
```

@@

**TASK 5**:   
Using the web-based effect size calculator, estimate a few other effect sizes using test (inferential) statistics reported in **Sadd2006.pdf**.

@@

The *compute.es* function inputs and names are as follows:   
 * ANCOVA F-test: "a.fes()""   
 * ANCOVA means: "a.mes()"   
 * ANCOVA means (pooled sd): "a.mes2()"   
 * ANCOVA p-value: "a.pes()"    
 * ANCOVA t-test: "a.tes()"   
 * Chi-squared (1 df): "chies()"   
 * Correlation: "res()"    
 * d-statistic: "des()"    
 * Failure group (binary): "failes()"    
 * F-test: "fes()"   
 * Log odds ratio: "lores()"    
 * Means: "mes()"    
 * Means (pooled sd): "mes2()"   
 * Proportions (binary): "propes()"    
 * p-value: "pes()""    
 * t-test: "tes()""

To learn more see the package vignette or https://www.rdocumentation.org/packages/compute.es/versions/0.2-4/topics/compute.es-package
